Workflow for Ecov Recruitment Analysis

### 2024-02-01 Ecov_study/recruitment_functions/Workflow_Ecov_Recruitment_Project.Rmd
Update Workflow_Ecov_Recruitment_Project.Rmd
fixing url for workflow

---
title: "Workflow for Ecov Recruitment Analysis"
output: html_notebook
---

<!-- This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.  -->

@@

>>>>

---
title: "Workflow for Ecov Recruitment Analysis"
output:
  html_document:
    df_print: paged
---
 Note: you can view this as a rendered html file, just click on the file and when it opens (as raw source code) just pre-pend this in front of the url: https://htmlpreview.github.io/?
<!-- This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.  -->

@@

## View html version <a href="https://htmlpreview.github.io/?https://github.com/timjmiller/SSRTWG/blob/main/Ecov_study/recruitment_functions/Workflow_Ecov_Recruitment_Project.html"> here</a>.
